### 2015-07-22 analysis/e5_analysis.Rmd
trying to break down literal listener semantics - just getting started

```{r}
rm(list=ls())
source("analysis/useful_dplyr.R")
library("rjson")
```

@@

>>>>

```{r}

rm(list=ls())
#setwd("~/Desktop/Projects/scalar_implicature/")
source("analysis/useful_dplyr.R")
library("rjson")
```

@@

# Histograms of agreement bins
```{r}
raw.scales <- d %>%
  mutate(stars = as.numeric(as.character(stars))/20) %>%
  group_by(scale, degree, stars)

raw.scales = raw.scales[
  order(raw.scales[,2], raw.scales[,3], raw.scales[,4]),]
raw.scales %>% gather()

barplot(raw.scales[which(
  raw.scales[,"scale"] == "good_excellent"
  & raw.scales[,"degree"] == "low"
  & raw.scales[,"stars"] == 1), ]$judgment)

?gather
library(dplyr)
# From http://stackoverflow.com/questions/1181060
stocks <- data.frame(
  time = as.Date('2009-01-01') + 0:9,
  X = rnorm(10, 0, 1),
  Y = rnorm(10, 0, 2),
  Z = rnorm(10, 0, 4)
)
?spread
gather(stocks, stock, price, -time)
stocksm <- stocks %>% gather(stock, price, -time)
stocksm %>% spread(stock, price)

# for reference -------->
ms <- d %>%
  mutate(stars = as.numeric(as.character(stars))/20) %>%
  group_by(scale, degree, stars) %>%
  summarise(cil = ci.low(judgment), 
            cih = ci.high(judgment), 
            judgment = mean(judgment), 
            p = (judgment - 1)/4)
# for reference -------->
```

# Gaussian Analysis 7-21-15
```{r}
# Just having a look using hard coded mean and var from e5a data
# Note: e5a data looks at counts of likert ratings over 4 on aggreableness
all.x = seq(1, 5, length=100)
all.y = dnorm(x, mean=4.537037037, sd=sqrt(0.285665295))  
plot(all.x,all.y, type="l", lwd=1, ylim = c(0, 1), col="blue")

some.x = seq(1, 5, length=100)
some.y = dnorm(x, mean=4.020522388, sd=sqrt(0.786892264))
plot(some.x,some.y, type="l", lwd=1)

lines(some.x, some.y, col="red")
```
